---
title: "Winery"
author: "Margherita Zamboni"
date: "6/19/2019"
output: 
  ioslides_presentation:
  smaller: true
  self_contained: true
---
# 

## What is WineRy?
- An app that allows you to select the best wine for your party! 
- Decide what's more important for you: __Ratings?__, __Price?__, __APK?__
- Are you interested in purchasing your bottle based on the __Country__ of origin?
- Are you looking for a particular __Variety__ of wine?

### WineRy will help you with that and much more!


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("../code/global.R", local = FALSE)

```


## Dataset - Our sources
- Wine ratings and descriptions were extracted from [tidytuesday repo](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-05-28)
- Details on prices and availibility were available at [System Bolaget](https://www.systembolaget.se/api/) and [Vinmonopolet](https://www.vinmonopolet.no/datadeling) APIs.


```{r data, echo = TRUE, eval=T}

str(vino[,4:8])

```

## Cleaning and merging data
- Bullet
- Bullet


## Plotting on map
- The map plot will inform you on
    + <font size="3">The **number**, **average price** of wines produced per country, </font>
    + <font size="3">The  of wine produced in each country </font>
    + <font size="3">The **average score** assigned for wines from each country </font>
- The plot was realised using: 
    + <font size="3">`library(ggplot2)`, `library(ggmap)`,  `library(maps)` </font>
 
```{r map, fig.height=3,fig.width=5, echo = F, eval=T}

ggplot()+
  borders("world", colour="gray80", fill="gray80") +
  geom_polygon(data = wine_map, 
               aes(x=long, y = lat, group = group, fill = mean_point)) +
  theme(
    axis.text = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    panel.grid = element_blank(),
    axis.title = element_blank(),
    legend.position = 'none') +
  coord_fixed() +
  scale_fill_viridis_c(alpha = 1, begin = 0, end = 1,
                         direction = 1, option = "D", aesthetics = "fill")


```

## Wine Overview 
- WineRy plots different variables in the interactive scatterplot to aid selection of wines that meet your requirements.
- Select for:
  + **Rating**
  + **Price**
  + **APK**
 
```{r dot, fig.height=3,fig.width=6, echo = F, eval=T, warning=F}
top <- vino %>% 
  filter(country == "Spain") %>% 
  group_by(variety) %>% 
  summarise(n=n(),
            mean_price = mean(price, na.rm = TRUE),
            mean_stars = mean(stars, na.rm = TRUE)) %>% 
  arrange(desc(n)) %>%
  top_n(n=3, wt=n) %>% pull(variety)

vino %>% 
  filter(country == "Spain")  %>% 
  group_by(variety) %>% 
  mutate(n=n(),
        mean_price = round(mean(price, na.rm = TRUE),digits = 2),
        mean_stars = round(mean(stars, na.rm = TRUE), digits = 1),
        color = case_when(variety == top[1] ~ paste("1",variety, mean_price, "/", mean_stars, sep = " "),
                          variety == top[2] ~ paste("2",variety, mean_price, "/", mean_stars, sep = " "),
                          variety == top[3] ~ paste("3",variety, mean_price, "/", mean_stars, sep = " "),
                          TRUE ~ "etc.")) %>% 
  ggplot(aes(x = stars, y = price))+
    geom_jitter(aes(fill= color),
                width = 0.2, height = 0.2, 
                shape=21,size=3,stroke=0.8,
                #fill="white",
                color = "#29B00E",
                show.legend = TRUE)+
    geom_smooth(method="loess",se=F,color="red",size=0.6, show.legend = FALSE)+  
    labs(title = "Wine rating per price")+
    xlab("Rating")+
    ylab("Price (USD)") +
    xlim(0,5)+
    guides(color = guide_legend(nrow = 2))+
    scale_fill_manual(values = c("red", "orange", "yellow", "grey60"))+
    theme(legend.position = "bottom",
        panel.grid.minor=element_blank(),
        panel.grid.major.x=element_blank(),
        panel.background=element_blank(),
        panel.border=element_blank(),
        legend.title=element_blank(),
        axis.title=element_text(face="italic"),
        axis.ticks.y=element_blank(),
        axis.ticks.x=element_line(color="grey60"),
        plot.title=element_text(face="bold", hjust=0.5))

```

## Details for your favourite wine
- Select and learn more about your favourite wine

```{r spider, fig.height=3,fig.width=3, echo = F, eval=T, warning=F, message=F}


names(demo) <- gsub("taste_", "", names(demo))
substr(names(demo), 1, 1) <- toupper(substr(names(demo), 1, 1))
    
demo=rbind(rep(1,5) , rep(0,5) , demo)
demo[3,] <- demo[3,]/12
    
radarchart(demo, axistype=1 , 
               #custom polygon
               pcol= "#F28C26",
               pfcol=rgb(0.949, 0.549, 0.149, 0.3),
               plwd=4 , plty=1,
               #custom the grid
               cglcol="grey", cglty=1, axislabcol="grey", cglwd=0.8,
               #custom labels
               vlcex=0.8 )

chardonnay_description <- read.csv("../data/chardonnay_descr.csv", header = T)
library(knitr)
library(kableExtra)
kable(chardonnay_description, col.names = c("", "Your Favourite Wine")) %>%
  kable_styling(bootstrap_options = c("striped"),full_width = F, position = "float_right")

```
