---
title: "Winery"
author: "Margherita Zamboni"
date: "6/19/2019"
output: ioslides_presentation
---
# 

## What is WineRy?
- An app that allows you to select the best wine for your party! 
- Decide what's more important for you: __Ratings?__, __Price?__, __APK?__
- Are you interested in purchasing your bottle based on the __Country__ of origin?
- Are you looking for a particular __Variety__ of wine?

### WineRy will help you with that and much more!


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("../code/global.R", local = FALSE)

```


## Dataset - Our sources
- Wine ratings and descriptions were extracted from [tidytuesday repo](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-05-28)
- Details on prices and availibility were available at [System Bolaget](https://www.systembolaget.se/api/) and [Vinmonopolet](https://www.vinmonopolet.no/datadeling) APIs.


```{r data, echo = TRUE, eval=T}

str(vino[,4:8])

```

## Cleaning and merging data
- Bullet
- Bullet


## Plotting on map
- The map plot will inform you on
    + <font size="3">The **number**, **average price** of wines produced per country, </font>
    + <font size="3">The  of wine produced in each country </font>
    + <font size="3">The **average score** assigned for wines from each country </font>
- The plot was realised using: 
    + <font size="3">`library(ggplot2)`, `library(ggmap)`,  `library(maps)` </font>
 
```{r map, fig.height=3,fig.width=5, echo = F, eval=T}

ggplot()+
  borders("world", colour="gray80", fill="gray80") +
  geom_polygon(data = wine_map, 
               aes(x=long, y = lat, group = group, fill = mean_point)) +
  theme(
    axis.text = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    panel.grid = element_blank(),
    axis.title = element_blank(),
    legend.position = 'none') +
  coord_fixed() +
  scale_fill_viridis_c(alpha = 1, begin = 0, end = 1,
                         direction = 1, option = "D", aesthetics = "fill")


```

## Wine Overview 
- WineRy plots different variables in the interactive scatterplot to aid selection of wines that meet your requirements 
 
```{r dot, fig.height=3,fig.width=6, echo = F, eval=T}

p1 <- ggplot(vino, aes(stars)) + 
      geom_bar(fill = "white", color = "#29B00E") +
      labs(title = "Wine rating")+
      xlab("Rating")+
      ylab("")+
      xlim(0,5)

```
